---
title: "Networking the ETYS"
author: "Jonathan Bourne"
date: "2 May 2017"
output: html_document
---

zico kolter-carnegie mellon

check out the network tools package

Not all the nodes are listed as sites

We can Work out the voltage, by ranking the MVA of the node and assigning it the same rank as the ranked V of the substation, using this we can say that we know the voltage at each point.

We assign the known loads to the nodes
and randomly assign the generators to nodes in the matching substations
We then solve a series of simultaneous equations where we have the matrix formula V=ZI and also know that V=0 at transmission nodes and V = rank line V at the node.

This means I have to 
assign a V to each node
match loads 
match generators

I can try using a simplified/made up version
This might also mean that when I want to use multiple voltage levels I end up having to iterate across sub-nets


```{r Setup}
packages <- c("tidyverse", "igraph","readr","readxl", "broom", "zoo", "stringr", "xtable")

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)


lapply(packages, library, character.only = TRUE)


#Set up file system to read the correct folders this switches between aws and windows mode

basewd<- "/home/jonno/Dropbox/Jonathan Bourne Phd Folder"
datafile<- "/home/jonno/Dropbox/Jonathan Bourne Phd Folder/ETYSAppendixB"
Functions <-"/home/jonno/Create_ETYS_network/Functions"

list.files(Functions) %>% map(~source(file.path(Functions,.x)))

LatexFigs <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Data problems with the ETYS/Figures"

```


#Loading and creating a structure for the data

```{r}
#create the path to the file
path <- file.path(datafile, "ETYS 2016 Appendix B.xlsx")


#Create a list of all the sheets in the file

AllData <- path %>% 
  excel_sheets(.) %>%
lapply(., read_excel, path = path, skip = 1, trim_ws = TRUE ) %>%
  map(~.x %>% setNames(make.names(names(.))))

#break out the sheet names

AllData[[1]] <- AllData[[1]] %>% 
  setNames(c("Table", "Title")) %>% 
  filter(complete.cases(.)) %>%
  mutate(Table = replace(Table, Table=="Table", "Index"), 
         element = 1:(n())) #provides list element reference

names(AllData) <- AllData[[1]]$Table

View(AllData$Index)

```

#Create base data
```{r}

Substation <- StackList(2:4) %>%
  mutate(Site.Code = str_trim(Site.Code),
         Site.Name = str_trim(Site.Name)) #remove leading and trailing whitespace which causes problems with analysis.

Circuits <- StackList(6:8)

names(AllData[[16]])[1:2] <-c("Node1", "Node2") #The name had been written differently to the other two
Transformers <- StackList(14:16)

#The RCE needs a lot of treatment as there are formatting differences and also the bind_rows part of map_df doesn't coerce, which is annoying.
names(AllData[[24]])[4] <-"MVAr.Generation"
names(AllData[[23]])[5] <-"MVAr.Absorption"
names(AllData[[24]])[5] <-"MVAr.Absorption"

AllData[[22]]$MVAr.Absorption<- AllData[[22]]$MVAr.Absorption %>%gsub("[^A-Z0-9]", "", ., ignore.case = TRUE)


RCE<- AllData[22:24] %>% map(~.x %>% RemoveSymbols %>% 
                                 mutate(Unit.Number = as.character(Unit.Number),
                                        Connection.Voltage..kV. = as.character(Connection.Voltage..kV.)))%>%
  map2_df(.x =.,
                     .y = names(.),
                     ~ .x %>% 
                      mutate(Table =.y ) )

```

#Create change data

```{r}
circuits_change <-  StackList(10:12)

names(AllData[[20]])[1:2] <-c("Node1", "Node2") #The name had been written differently to the other two
transformers_change <- StackList(18:20)
```


#Understanding the Substation data
```{r}

#I'm not sure why the OFTO is different and therfore cannot be incuded

#How many site codes are there?

length(unique(Substation$Site.Code))

#Howmany when the results are split by organisation?

Substation %>% split(.$Table) %>% map_dbl(~length(unique(.x$Site.Code))) %>% sum

#The results of these two tests show that the different tables contain identical codes. These need to be identified.

OverlappingSubstations <- Substation %>% split(.$Table) %>% 
  map(~data.frame(unique(Substation$Site.Code) %in% .x$Site.Code))  %>%
  bind_cols() %>% setNames(unique(Substation$Table))%>% 
  mutate(tots = rowSums(.)) %>%
  bind_cols(data.frame(Site.Code = unique(Substation$Site.Code)),.) %>%
  filter(tots>1) %>% left_join(., Substation)

#This overlapping data frame shows which nodes overlap across tables. It also shows that the different organisation may not have the same voltages. For example Invernan (INVR) SHE has 132 and 33 Kv connections whilst SPT has 275kv. 
#The overlapping table also reveals an issue with the naming convention. the code LOCH is used for both the substation by Lochay hydro plant and also the substation by Loch Hill windfarm which are over 100 miles apart. 

#Checking for multiple uses of the same code in different substations to see how many times events like "LOCH" occur.

DoubleNames <- Substation %>% group_by(Site.Code, Site.Name) %>% summarise(counts =n()) %>% 
  ungroup %>%
  group_by(Site.Code) %>% mutate(reps = n()) %>% ungroup %>% filter(reps>1)

DoubleNames %>% select(Site.Code, Site.Name) %>%
  xtable()

#This is a common occurance for the doubles, there are two occurances one the name the other with "windfarm" added on. This needs to be investigated to check whether they are in the same physical location or not. 
Substation %>% filter(Site.Code == "BIRN")

#Although several of the doubles are spelling mistakes.
#Further investigation needs to be made to see whether these doubles are the same point or are different physical locations.

```


#OFTO

```{r}


CircuitsOFTO <- AllData[[9]] %>%
  rename(Node1 = Node.1, Node2 =Node.2, Cable.Length..km. = Length..km., Circuit.Type = Type) %>%
  mutate(OHL.Length..km. = 0,
         Winter.Rating..MVA. = Rating..MVA.,
         Spring.Rating..MVA. = Rating..MVA.,
         Summer.Rating..MVA. = Rating..MVA.,
         Autumn.Rating..MVA. = Rating..MVA.,
         Table = "B.2.1d") %>% 
  select(-OFTO, -Station, -Rating..MVA., -Voltage..kV.  ) #voltage ius removed, although it is very useful, for consistancy 

Circuits <- bind_rows(Circuits, CircuitsOFTO)


TransformersOFTO <- AllData[[17]] %>%
  mutate(Table = "B.3.1d") %>% 
  select(-OFTO, -Site, -Rating..MVA.) %>%
  setNames(c("Node1","Node2" ,"R....on.100MVA.","X....on.100MVA.","B....on.100MVA.","Rating..MVA.","Table"  ))


Transformers <- Transformers %>% 
  mutate(Rating..MVA. = as.character(Rating..MVA.)) %>%
  bind_rows(.,TransformersOFTO)

RCEOFTO <- AllData[[25]] %>%
  mutate(MVAr.Generation =  as.numeric(MVAr.Generation),
         MVAr.Absorption =  as.numeric(MVAr.Generation),
         Table = "B.4.1d") %>%
  select(-OFTO,-Tapping)


RCE  <- bind_rows(RCE, RCEOFTO)

```



#Make a circuit network

Some experiments to get a sensible looking network working


One idea may be to build up a single site into a complete graph, a good example would be harker as it has 8 units.

```{r}
#find the substation with the most occurances
data_frame(Names =  c(str_sub(Circuits$Node1,  1,4),str_sub(Circuits$Node2,  1,4))) %>%
  group_by(Names) %>%
  summarise(Counts = n()) %>%
  arrange(-Counts)

#sublist <- Circuits %>% filter(grepl("ABNE", .$Node1)|grepl("ABNE", .$Node2))

#This network has a lot of isolated nodes
graph1 <-graph_from_edgelist(as.matrix(Circuits[,1:2]), directed = FALSE)
degree(graph1) %>% table
plot(graph1)

#To get around the above problem I will only use the 4 character identifier to construct the network.

graph2 <- Circuits %>% mutate(Node14 = str_sub(Node1,  1,4),
                    Node24 = str_sub(Node2,  1,4))
graph2 <- graph_from_edgelist(el =graph2 %>% select(Node14, Node24) %>% as.matrix, directed = FALSE)
degree(graph2) %>% table #huge reduction in isolated nodes
graph2 %>% 
  simplify(., remove.multiple = F, remove.loops = T) %>% 
  plot(., edge.arrow.size=.4, vertex.label=NA)

```

#Fullname
One issue is that it is difficult to know what everything is linking two, in order to get a greater under standing I will try to match the full names to everything else and see how many have a match and how many don't

```{r}

FullnameCounts <- list(
  data_frame(Name = c(Circuits$Node1, Circuits$Node2), Type = "Circuits"),
data_frame(Name = c(Transformers$Node1, Transformers$Node2), Type = "Transformers"),
data_frame(Name =RCE$Node, Type = "RCE")) %>%
  bind_rows %>%
group_by(Name, Type) %>%
  summarise(Count = n()) %>%
  arrange(-Count) %>%
group_by(Name) %>%
  mutate(Total = sum(Count),
         TypeCounts = n()) %>% 
  ungroup

#Add in the amount of times a site appears
FullnameCounts <- FullnameCounts %>%
  mutate(Site = str_sub(Name, 1,4)) %>%
  group_by(Site) %>%
  mutate(SiteCount = sum(Count),
         SiteTypeCounts = unique(Type) %>% length) %>%
  ungroup


#Double connection is this right? means double transformer?
Transformers %>% 
  filter(Node1 == "BEAU1J"|Node2 == "BEAU1J")


#How many appear only once
 table(FullnameCounts$Count)



 #is everything that has a 3- also have a 33kv voltage?
 test <- FullnameCounts%>% 
  filter(grepl("AMUL", Name))
 
test <-  Substation %>% filter(Site.Code %in% test$Site) 
table(test$Voltage..kV.) 

sum( Substation$Voltage..kV. %in% test$Name)

```


#making a larger network using fullname counts
```{r}

graph1 <-bind_rows(Circuits, Transformers) %>%  
  .[,1:2] %>%
  as.matrix() %>% 
  graph_from_edgelist(., directed = FALSE)
degree(graph1) %>% table

plot(graph1)


g2 <- delete.vertices(graph1, clusters(graph1)[[1]]==1)
#The disconnected componants
plot(g2)


Substation %>% 
  filter(Site.Code == "CAFA")

Circuits %>% 
  filter(grepl("CAFA", Node1)|grepl("CAFA",Node2))

Transformers %>% 
  filter(grepl("CAFA", Node1)|grepl("CAFA",Node2))

#missing
Substation %>% 
  filter(Site.Code == "LINS")

test<- FullnameCounts %>% 
  filter(Site == "MOTA")

Substation %>% 
  filter(Site.Code == "LISD")

```




```{r}
ABNEgraph <-SubGraph("ABHA")

BEAUgraph <-SubGraph("BEAU")
degree(BEAUgraph) %>% table

#This graph looks like it has doubles between BEAU2J/BEAU1J why? is this a double circuit? What can I do about it?
plot(BEAUgraph)

z<- SubGraph("HARK")

#I tried to make a plus 1 gtraph but it didnt work very well.
test2<- paste(unique(str_sub(V(z)$name,1,4)) ,collapse = "|")

#For the document the data problems...

FullnameCounts %>% filter(Site =="BEAU")

Substation %>% filter(Site.Code=="BEAU") %>%
  xtable
z <- SubGraph("BEAU")

setwd(LatexFigs)
pdf('BEAU.pdf')
plot(z)
dev.off()


z <- SubGraph("DRAX")

setwd(LatexFigs)
pdf('Drax.pdf')
plot(z)
dev.off()


z <- SubGraph("AMUL")
setwd(LatexFigs)
pdf('AMUL.pdf')
plot(z)
dev.off()

setwd(datafile)
```


#Load the demand dataset
```{r}

demand <- read_excel(file.path(datafile,"ETYS16 AppG demand data.xlsx"), skip = 7)

#Percent f demand that matches a nodes
sum(unique(demand$Node) %in% unique(FullnameCounts$Name))/length(unique(demand$Node))

#check using just site this matches loads
sum(str_sub(unique(demand$Node),1,4) %in% str_sub(unique(FullnameCounts$Name),1,4))/length(unique(demand$Node))


demand2 <- FullnameCounts %>% filter(grepl("KEAR", Name))

test <- FullnameCounts %>% filter(Name %in% unique(demand$Node))

demand2 <- demand %>% filter(grepl("BEAU", Node))




```

Generateion
```{r}
Substation %>% filter(grepl("kear",Site.Name, ignore.case = TRUE))

```


#Substation graph

This graph uses only substations

```{r}
Name <- "BEAU"

SubStatGraph <-bind_rows(Circuits, Transformers) %>%
  # filter(grepl(Name, Node1)|grepl(Name,Node2)) %>%
  mutate(Node1 = str_sub(Node1, 1, 4),
         Node2 = str_sub(Node2, 1, 4)) %>%
  .[,1:2] %>%
  as.matrix() %>% 
  graph_from_edgelist(., directed = FALSE)
degree(SubStatGraph) %>% table


l <- layout_with_drl(SubStatGraph, options=list(simmer.attraction=0))

minC <- rep(-Inf, vcount(SubStatGraph))
maxC <- rep(Inf, vcount(SubStatGraph))
minC[1] <- maxC[1] <- 0
co <- layout_with_fr(SubStatGraph, minx=minC, maxx=maxC,
                                  miny=minC, maxy=maxC)
SubStatGraph %>%
  simplify(., remove.multiple = T, remove.loops = T) %>% 
    plot(., layout = co,vertex.size=.8, edge.arrow.size=.4, vertex.label=NA)

SubStatGraph %>%
  simplify(., remove.multiple = T, remove.loops = T) %>% 
plot(., layout = l, vertex.label = NA,vertex.size=.8, edge.arrow.size=.4)

SubStatGraph %>% 
  simplify(., remove.multiple = T, remove.loops = T) %>% 
  plot(.,vertex.size=.8, edge.arrow.size=.4, vertex.label = NA)


```


#Looking at impedance

It doesn't make sense that connections like ABNE1Q-ABNE1R have a reactance but 0 susceptance.

The reactance is a percentage which relies on the power to have a value. But the impedance matrix combines with power/V/A to create useful stuff, so how is this not a circular logic?

you also need a transmission matrix



```{r}
 Impedance <- bind_rows(mutate(Circuits, MVA=Spring.Rating..MVA.,
                               Type = "Circuit"), 
                        mutate(Transformers, MVA = Rating..MVA.,
                               Type = "Transformer")) %>%
  select(Node1, Node2, R....on.100MVA., X....on.100MVA., B....on.100MVA.,
         MVA, Type) %>%
    mutate(
    
        R = R....on.100MVA./100,
        X = X....on.100MVA./100,
        B = B....on.100MVA./100,
        MVA = round(MVA, 0),
        ImpInvS = 1/B,
         ImpRX =  complex(real = R, imaginary = X),
         ImpInvS2 = 1/(B*MVA),
         ImpRX2 = complex(real = R, imaginary = X)*MVA,
    B2 = -X/(R^2+X^2)) %>%
  #create the voltage matching
  mutate(Node1b = str_sub(Node1, 1, 4),
         Node2b = str_sub(Node2, 1, 4)) 

imp2 <- bind_rows(Impedance[,c(16,6)], rename(Impedance[,c(17,6)], Node1b= Node2b)) %>%
  group_by(Node1b, MVA) %>%
  summarise(Counts = n()) %>%
  group_by(Node1b) %>%
  mutate(rank = rank(MVA))
#ABTH has 5 power levels but only two voltage levels so this won't work
Substation %>% filter(Site.Code=="ABTH")

#Create impedance using 1/B
Impmat<- Impedance %>% 
  select(Node1,Node2, ImpInvS) %>%
  CreateImpedance

#Create impedance using X
Impmat2 <- Impedance %>% 
    mutate(X2 = X*MVA ) %>%
  select(Node1,Node2, X2) %>%
  CreateImpedance


#Create addmitance using 1/X
Admat<- Impedance %>% 
    mutate(B2 = 1/(X*MVA) ) %>%
  select(Node1,Node2, B2) %>%
  group_by(Node1,Node2) %>%   #trying to remove multuple connections
  summarise(B2 = sum(B2)) %>%
  CreateImpedance



#Is junk
#Admat2 <- solve(Admat)


MinVolt <- Substation %>%
  group_by(Site.Code) %>%
  summarise(V = min(Voltage..kV.))

Voltagemaker <- left_join(data.frame(Node = colnames(Admat)), 
                          demand, by = "Node") %>%
  group_by(Node) %>%
  mutate_all(funs(ifelse(is.na(.),0,1)))%>%
  ungroup %>% 
  .[,c(1,3)] %>%
  mutate(Site.Code = str_sub(Node, 1,4)) %>%
  left_join(., MinVolt, by = "Site.Code") %>%
  mutate(V = ifelse(is.na(V),0, V)) #some nodes don't have a site, these are set to 0

#I will add load in Drax, DRAX42
#Didcot -
#Dounray

#building in edgename numbers helps the multiples but doesn cure

Transmission <- Impedance %>%
  CreateTransmission(., "Node1", "Node2", "B2")

#Doesn't work
Current <- Transmission %*% Admat %*% Voltagemaker$V

```


#Create voltges

I can probably create a site to site voltage network

```{r}

test<- Substation %>% 
  group_by(Site.Code) %>%
  mutate(rank = rank(Voltage..kV.)) %>%
  filter(Site.Code =="EXET"|Site.Code =="ABHA")

test<- Substation %>% 
  group_by(Site.Code) %>%
  mutate(rank = rank(Voltage..kV.))


```

