---
title: "Networking the ETYS"
author: "Jonathan Bourne"
date: "2 May 2017"
output: html_document
---


Current situation

There is an Admission matrix, thre is a Transmission Matrix. Both are Wrong
There is a Power Injection vector that is balenced
The DC power flow equation produces numeric results although they are wrong

Next step
How are the Ad and Trans mats wrong?

What centrality measure functions can I make?
basic
electrical distance
  How do I measure electircal distance

Entropy
  Same for entropy
  
```{r}
setwd("/home/jonno/Create_ETYS_network/SubCode")
source("Setup.R")

source("LoadData.R")

source("CreateCoreData.R")

#There is missing data especially from the susceptance column this is being filled in with 0
Circuits$B....on.100MVA.[is.na(Circuits$B....on.100MVA.)]<-0
Transformers[is.na(Transformers)] <- 0

```



Extracting trasnport data
```{r}

trans1 <-TransportData[,1:16] %>% 
  filter(!is.na(Bus.ID))

#In this data the production and generation is already matched
sum(trans1$Demand)  
sum(trans1$Generation.A.....Peak.Security...Transport.Model.)  
sum(trans1$Generation.B.....Year.Round...Transport.Model.)

trans2 <- TransportData[,17:59] %>% 
  filter(!is.na(Bus.1))
  
#Do the generation and or deman in trans1 match the nodes in the trans2?

Trans2Nodes <- unique(c(trans2$Bus.1, trans2$Bus.2))

#perfect match, this should be surprising but it is still good.
sum(trans1$Bus.Name %in% Trans2Nodes)/nrow(trans1)




SubStatGraph2 <-trans2 %>%
  mutate(Node1 = str_sub(Bus.1, 1, 4),
         Node2 = str_sub(Bus.2, 1, 4)) %>%
  select(Node1, Node2) %>%
  as.matrix() %>% 
  graph_from_edgelist(., directed = FALSE)

SubStatGraph2 %>% 
  simplify(., remove.multiple = T, remove.loops = T) %>% 
  plot(.,vertex.size=.8, edge.arrow.size=.4, vertex.label = NA)

length(V(SubStatGraph2))


SubStatGraph2 <-trans2 %>%
  mutate(Node1 = Bus.1,
         Node2 = Bus.2) %>%
  select(Node1, Node2) %>%
  as.matrix() %>% 
  graph_from_edgelist(., directed = FALSE)

SubStatGraph2 %>% 
  simplify(., remove.multiple = T, remove.loops = T) %>% 
  plot(.,vertex.size=.8, edge.arrow.size=.4, vertex.label = NA)
length(V(SubStatGraph2))


```


Create Substation Graph
```{r}

SubStatGraph <-bind_rows(Circuits, Transformers) %>%
  mutate(Node1 = str_sub(Node1, 1, 4),
         Node2 = str_sub(Node2, 1, 4)) %>%
  .[,1:2] %>%
  as.matrix() %>% 
  graph_from_edgelist(., directed = FALSE)

#degree of site graph
degree(SubStatGraph) %>% table


#Plot graph
SubStatGraph %>% 
  simplify(., remove.multiple = T, remove.loops = T) %>% 
  plot(.,vertex.size=.8, edge.arrow.size=.4, vertex.label = NA)
```


Compare Node matches across the different Data sets


#Full Name Counts
```{r}
FullnameCounts <- list(
  data_frame(Name = c(Circuits$Node1, Circuits$Node2), Type = "Circuits"),
data_frame(Name = c(Transformers$Node1, Transformers$Node2), Type = "Transformers"),
data_frame(Name =RCE$Node, Type = "RCE")) %>%
  bind_rows %>%
group_by(Name, Type) %>%
  summarise(Count = n()) %>%
  arrange(-Count) %>%
group_by(Name) %>%
  mutate(Total = sum(Count),
         TypeCounts = n()) %>% 
  ungroup

#Add in the amount of times a site appears
FullnameCounts <- FullnameCounts %>%
  mutate(Site = str_sub(Name, 1,4)) %>%
  group_by(Site) %>%
  mutate(SiteCount = sum(Count),
         SiteTypeCounts = unique(Type) %>% length) %>%
  ungroup
```



```{r}

#Percent f demand that matches a nodes
sum(unique(DemandData$Node) %in% unique(FullnameCounts$Name))/length(unique(DemandData$Node))

#check using just site this matches loads
#This matches 97% of the demand and is therefore pretty useful. for a site based analysis.
sum(unique(DemandData$Site) %in% FullnameCounts$Site)/length(unique(DemandData$Site) )

#Match rate is a joke
sum(unique(GenerationData$Node.1) %in% FullnameCounts$Name)/length(unique(GenerationData$Node.1) )


#Match Rate is pretty good!
sum(unique(GenerationData$Site) %in% FullnameCounts$Site)/length(unique(GenerationData$Site) )

#Excluding NA's I'm pretty Happy
G2 <- GenerationData %>%
  filter(!is.na(Site))
(sum(unique(G2$Site) %in% FullnameCounts$Site)/length(unique(G2$Site) ))

#Terrible
sum(LocalAssetData$Bus.Name %in% FullnameCounts$Name)/length(unique(LocalAssetData$Bus.Name) )

#Match Rate is slightly lower than the Generation Data set.
sum(unique(str_sub(LocalAssetData$Bus.Name,1,4)) %in% FullnameCounts$Site)/length(unique(str_sub(LocalAssetData$Bus.Name,1,4)) )

```

#Create a demand generation Vector
```{r}

G2 <- GenerationData %>%
  group_by(Site) %>%
  summarise(MWGen =  sum(Generation.Base....Tariff.Model.TEC., rm.na = TRUE))

D2 <- DemandData %>%
  group_by(Site) %>%
  summarise(MWDem = sum(MW, na.rm = TRUE))

InjectionVector <- FullnameCounts %>% select(Site) %>%
  group_by(Site) %>%
  summarise(count = n()) %>%
  left_join(D2) %>%
  left_join(G2) %>%
  mutate_if(is.numeric, funs(ifelse(is.na(.),0,.))) %>%
  mutate(NetPower = MWGen-MWDem)



```

Create a data frame of Impedance information necessary to produce the overall graph


#Susceptances are over 100% and all of the ones that are are from B.2.1c

```{r}
TranformerMin <- Transformers$Rating..MVA. %>% str_split(., "/") %>% map_dbl(~.x %>% as.numeric %>% min)

 Impedance <- bind_rows(mutate(Circuits, MVA=Spring.Rating..MVA.,
                               Type = "Circuit"), 
                        mutate(Transformers, MVA = Rating..MVA.,
                               Type = "Transformer",
                        #insert conveted MVA
                               MVA = TranformerMin)) %>%
  #restrict to site only
  mutate(Node1b = str_sub(Node1, 1, 4),
         Node2b = str_sub(Node2, 1, 4))  %>%
   #remove self connections
   filter(Node1b !=Node2b) %>%
   #convert the values to actual percentages
   mutate(R = R....on.100MVA./100,
        X = X....on.100MVA./100,
        B = B....on.100MVA./100)
 
 #All NGET all Circuit... what does this mean? apart from probably data error
 Impedance %>% filter(B>1) %>% .$Table %>% table()
 Impedance %>% filter(B>1) %>% .$Type %>% table()
 
 #Filling in missing and Errors
 #There are a lot of NA and obviously missing information. 
 #In this section I will take various actions to try and reduces the amount of wrongness in the resulting data
 
 Impedance <- Impedance %>%
  select( Node1b, Node2b, R, X, B,
         MVA, Type) %>%
   
   #Rounds the smallest number to 4 sig digs
   #When the Susceptance is NA or zero put the largest Susceptance
  #When X or R are 0 or NA put in the lowest none zero value, this will also create a large admittance
  #When MVA is missing or 0 put the largest mVS
     mutate(B = round(B,4),
       B = MissingOrZero(B, type = "max"),
           R =  MissingOrZero(R, type = "max"),
           X =  MissingOrZero(X, type = "max"),
           MVA = MissingOrZero(MVA, "max"))
  
 

 Impedance <- Impedance  %>%
    mutate(
        MVA = round(MVA, 0),
        ImpInvS = 1/B,
         ImpRX =  complex(real = R, imaginary = X),
         ImpInvS2 = 1/(B*MVA),
         ImpRX2 = complex(real = R, imaginary = X)*MVA,
    B2 = -X/(R^2+X^2))
 #remove missing is no longer used at is can mess up the structure of the network
# filter(!is.na(MVA))

 #The results of the above cleaning are a crazy mess, the two different measures of susceptance have no correlation.
cor(Impedance$B, Impedance$B2)
 
```



To balance the output each componant needs to have demand and production balanced IF there is demand & production in the same componant

```{r}
#95% of all nodes are in the main componant
components(SubStatGraph)$csize/573

#Not Graph explore why later
InjectionVector %>%
filter(!(Site %in% V(SubStatGraph)$name))

InjectionVector %>%
filter(Site %in% V(SubStatGraph)$name) %>%

  #we will start simply and tune down MWGen so that it matches MWDem
CompInject <- data_frame(Site = names(components(SubStatGraph)$membership) %>% unlist,
           Componant = components(SubStatGraph)$membership %>% unlist) %>%
  left_join(InjectionVector, by ="Site") %>%
  group_by(Componant) %>%
  mutate(TotMWDem = sum(MWDem),
         TotMWGen = sum(MWGen),
         diff = ifelse(TotMWDem==0 | TotMWGen==0,0,TotMWDem/TotMWGen),
         AdjNetPower = diff*MWGen-MWDem)

#WE can see that the other small componants have no generation or demand
CompInject %>%
  group_by(Componant) %>%
  summarise(MWDem = sum(MWDem),
            MWGen = sum(MWGen)) %>%
  mutate(diff = ifelse(MWDem==0 | MWGen==0,0,MWDem/MWGen))



  


```


```{r}

 #Subgraph test

 Impedance3 <- Impedance %>% 
  filter( Node1b %in% KNearestNodes(SubStatGraph, "BEAU", 1)| Node2b %in% KNearestNodes(SubStatGraph, "BEAU", 1) )


 
 Admat<- Impedance %>% 
    mutate(B2 = 1/(X*MVA) ) %>%
  select(Node1b,Node2b, B2) %>%
  group_by(Node1b,Node2b) %>%   #trying to remove multuple connections
  summarise(B2 = max(B2, na.rm = TRUE)) %>%
  CreateImpedance
Admat[is.na(Admat)] <- 0 #Na's are created
Admat[!is.finite(Admat)] <- 0 #Non finite numbers created by dividing by 0
 

 Transmission <- Impedance %>% 
  select(Node1b, Node2b, B2) %>%
  group_by(Node1b, Node2b) %>%
  summarise(B2 = max(B2, na.rm = TRUE))  %>%
  CreateTransmission(., "Node1b", "Node2b", "B2")
 
  Current <- Transmission %*% Admat %*% InjectionVector$NetPower[InjectionVector$Site %in% colnames(Admat)]
  Current <- Transmission %*% Admat %*% CompInject$AdjNetPower[CompInject$Site %in% colnames(Admat)]
 
#Why are some numbers so big?  
Power <- Admat %*% InjectionVector$NetPower[InjectionVector$Site %in% colnames(Admat)]
 
#Node power is much less outrageos
#Suggests that the Admat and Transmission matrices are wrong and the combination makes things get out of control
Power <- Admat %*% CompInject$AdjNetPower[CompInject$Site %in% colnames(Admat)]

Admat2 <-Admat
diag(Admat2) <-0

  solve(Admat[1:114,1:114])

solve(Admat[1:424,1:424])

table(Admat[424,])
Admat[424,][Admat[424,]!=0]

test<-Admat[rowSums(abs(Admat))==0,]


test <- Impedance %>% 
  filter(Node1b == "GWYW"|Node2b == "GWYW")
FullnameCounts$Name
```


#using Trans1

```{r}
 
#NewNodes <- KNearestNodes(SubStatGraph, "ABNE", 1)

#CompInject2 <- BalencedGenDem(SubStatGraph, InjectionVector, NewNodes)


Impedance2 <- trans2 %>%
  mutate(Y = 1/X..Peak.Security.) %>%
  select(Bus.1, Bus.2, Y)

 
 #It looks like using the B2 metric was causing major problems
 Admat<- Impedance2 %>% 
  group_by(Bus.1,Bus.2) %>%   #trying to remove multuple connections
  summarise(Y = max(Y, na.rm = TRUE)) %>%
  CreateImpedance

 plot(density(diag(Admat)))
 
 remove <- which.max(diag(Admat))
 Adinv<- solve(Admat[-remove, -remove])
 Admat2 <- Admat  
 Admat2[remove, remove] <- Admat2[remove, remove] + 50 # add in additional susceptance so it can be inverted
 
 Adinv<- solve(Admat[-remove, -remove]) 
 Adinv2<- solve(Admat2) 
 
 Transmission <- Impedance2 %>%
 group_by(Bus.1,Bus.2) %>%   #trying to remove multuple connections
  summarise(Y = max(Y, na.rm = TRUE)) %>%
  CreateTransmission(., "Bus.1", "Bus.2", "Y")

  Current <- Transmission %*% Admat %*% CompInject2$AdjNetPower[CompInject2$Site %in% colnames(Admat)]
 
#Why are some numbers so big?  
Power <- Admat %*% InjectionVector$NetPower[InjectionVector$Site %in% colnames(Admat)]


 test <- induced_subgraph(SubStatGraph, names(V(SubStatGraph)) %in% NewNodes)

 test %>% simplify %>% plot() 
 
 solve(Admat)
test<- solve(Admat[-3,-3])
 
rowSums(Admat) 

diag(Admat) <- diag(Admat)+1

solve(Admat)

```



Centrality
```{r}

CentralityMetrics <- data_frame(names(betweenness(SubStatGraph)),
           Centrality =betweenness(SubStatGraph))



EdgeCentrality <- data_frame(Centrality = edge.betweenness(SubStatGraph))


CentralityMetrics  %>% ggplot(.,aes(x=Centrality)) +geom_density()


```

