---
title: "Untitled"
author: "Jonathan Bourne"
date: "1 August 2017"
output: html_document
---

#Setup Chunk

```{r}
setwd("/home/jonno/Create_ETYS_network/SubCode")
source("Setup.R")

```


#Load Tariff and Trasnport
 
```{r}
KeepPath <- getwd()

#Load Tariff aka generation data
setwd(Tariff)

GenerationData <- read_excel("Tariff & Transport Model_2018_19 Tariffs_External.xlsm", sheet =10, skip = 33) %>%
  setNames(make.names(names(.))) %>%
  mutate(Site = str_sub(Node.1,1,4))

LocalAssetData <- read_excel("Tariff & Transport Model_2018_19 Tariffs_External.xlsm", sheet =11, skip = 11) %>%
  setNames(make.names(names(.)))

TransportData <- read_excel("Tariff & Transport Model_2018_19 Tariffs_External.xlsm", sheet =12, skip = 11) %>%
  setNames(make.names(names(.)))

setwd(KeepPath)
rm(KeepPath)
```

#Clean and seperate Transport

```{r}
trans1 <-TransportData[,1:16] %>% 
  filter(!is.na(Bus.ID))

trans2 <- TransportData[,17:59] %>% 
  filter(!is.na(Bus.1))
```



```{r}

NodeGraph <-trans2 %>%
  mutate(Node1 = Bus.1,
         Node2 = Bus.2) %>%
  select(Node1, Node2) %>%
  as.matrix() %>% 
  graph_from_edgelist(., directed = FALSE)

NodeGraph %>% 
  simplify(., remove.multiple = T, remove.loops = T) %>% 
  plot(.,vertex.size=.8, edge.arrow.size=.4, vertex.label = NA)
length(V(SubStatGraph2))

```

#Injection Vector
```{r}
InjectionVector <- trans1 %>% arrange(Bus.Name) %>% .$BusTransferB
```


#Create Impedance and Transmission matrix

parallel susceptances are added together. does this mean that when there are multiple lines connecting two nodes they should be added together and have the total capacity added together or should they be help seperate?

the removing of parallel cables may be causing some of the over capacity lines

```{r}
Impedance <- trans2 %>%
  mutate(Y = 1/X..Peak.Security.) %>%
  select(Bus.1, Bus.2, Y)

 
 #It looks like using the B2 metric was causing major problems
 Admat<- Impedance %>% 
  group_by(Bus.1,Bus.2) %>%   #trying to remove multuple connections
  summarise(Y = max(Y, na.rm = TRUE)) %>%
  CreateImpedance

remove <- which.max(diag(Admat))
Admat[remove, remove] <- Admat[remove, remove] + 50 # add in additional susceptance so it can be inverted
  
 Transmission <- Impedance %>%
 group_by(Bus.1,Bus.2) %>%   #trying to remove multiple connections
  summarise(Y = max(Y, na.rm = TRUE)) %>%
  CreateTransmission(., "Bus.1", "Bus.2", "Y")

```

Alternative calc
```{r}


df<- Impedance
StartNode <- "Bus.1"
EndNode <- "Bus.2"

AZero <-  Impedance %>%
  CreateTransmission(., "Bus.1", "Bus.2")

#remove Slack bus, usually the largest generator
SlackRef<-which.max(trans1$Generation.A.....Peak.Security...Transport.Model.)
trans1$Bus.Name[SlackRef] #name of node to be removed

A <- AZero[,colnames(A)!=trans1$Bus.Name[SlackRef]]


C <- LinePropertiesMatrix(Impedance, "Bus.1", "Bus.2")

B <- t(A) %*% C %*% A

InjectionVector2 <- trans1$BusTransferB[match(colnames(A), trans1$Bus.Name)]

PowerAlt <- C %*% A %*% solve(B) %*% InjectionVector2

```


#Power Flow

This contains really big numbers, is this right? The ordering of the multiplication could be wrong

```{r}
Power <- Transmission %*% Admat %*% InjectionVector

Current <- Admat %*% (trans1 %>% arrange(Bus.Name) %>% .$Voltage)

Power <- Power %>% data.frame(Link = rownames(.), Power = .) %>%
  #removes the link number as there are some nodes with multiple links between a single pair
  mutate(Link = sub("(-[0-9]$)", "", Link))

test <- trans2 %>%
  mutate(Link = paste(Bus.1, Bus.2, sep="-")) %>% 
  left_join(., Power, by = "Link") %>%
  mutate(Over = Power>Link.Limit)

#about a third of the lines are over charged.... why?
table(test$Over)

test2 <- test %>%
  mutate(Link.Type = tolower(Link.Type)) %>%
  group_by(Link.Type, Over) %>%
  summarise(counts = n()) %>%
  mutate(Over = tolower(Over)) %>%
  spread(key = Over, value = counts) %>%
  mutate(Total = true+false)

```


#Voltage Matching
Everyone matches to the same voltage unless it is a transformer.
There is an excpetion three types called construct also have different volatges, these could be also transformers under construction... this should be tested.
```{r}

Vmatch <- trans1 %>% select(Bus.Name, Voltage)

Vnet <- trans2 %>% 
  select(Bus.1, Bus.2, Link.Type) %>%
  left_join(., Vmatch, by = c("Bus.1"="Bus.Name")) %>%
  rename(Voltage.1 = Voltage) %>%
  left_join(., Vmatch, by = c("Bus.2"="Bus.Name")) %>%
  rename(Voltage.2 = Voltage)


Vnet2 <- Vnet %>% filter(Voltage.1 != Voltage.2)

  g <- graph.data.frame(Vnet[,1:2], vertices=Vmatch, directed=FALSE) %>%
  simplify(., remove.multiple = T, remove.loops = T) 
  
V(g)$color <- V(g)$Voltage

plot(g,vertex.size=5, edge.arrow.size=.4, vertex.label = NA)
  


```

