---
title: "Untitled"
author: "Jonathan Bourne"
date: "1 August 2017"
output: html_document
---

#Contact details charging team
01926 654633 or email charging.enquires@nationalgrid.com

I should change the graph so all information is encoded into it as graph attributes.

##Node attributes
Generated power <- theoretcial generated max
power demand
balanced power
name

##Edge attributes
Y
Power Limit
Power FLow

With the information above held in the graph each node would contain all necessary information for the analysis and would simplify a lot of the processes

#Setup Chunk

```{r}
setwd("/home/jonno/Create_ETYS_network/SubCode")
source("Setup.R")

```


#Load Tariff and Trasnport
 
```{r}
KeepPath <- getwd()

#Load Tariff aka generation data
setwd(Tariff)

GenerationData <- read_excel("Tariff & Transport Model_2018_19 Tariffs_External.xlsm", sheet =10, skip = 33) %>%
  setNames(make.names(names(.))) %>%
  mutate(Site = str_sub(Node.1,1,4))

LocalAssetData <- read_excel("Tariff & Transport Model_2018_19 Tariffs_External.xlsm", sheet =11, skip = 11) %>%
  setNames(make.names(names(.)))

TransportData <- read_excel("Tariff & Transport Model_2018_19 Tariffs_External.xlsm", sheet =12, skip = 11) %>%
  setNames(make.names(names(.)))

setwd(KeepPath)
rm(KeepPath)
```

#Clean and seperate Transport

```{r}
trans1 <-TransportData[,1:16] %>% 
  filter(!is.na(Bus.ID))

trans2 <- TransportData[,17:59] %>% 
  filter(!is.na(Bus.1)) %>%
  group_by(Bus.1, Bus.2) %>% #trying to stop the non-unique identifier problem
    mutate(Link = paste(Bus.1,Bus.2, 1:n(),sep = "-")) %>% #This allows multiple edges 
    #between the same node pair, it is not certain the data is always correct!
    ungroup %>%
  group_by(Bus.1, Bus.2) %>% #trying to stop the non-unique identifier problem
    mutate(Link = paste(Bus.1,Bus.2, 1:n(),sep = "-")) %>% #This allows multiple edges 
    #between the same node pair, it is not certain the data is always correct!
    ungroup  %>%
#set construct line limits really high
  mutate(Link.Type = tolower(Link.Type),
    Link.Limit = ifelse(Link.Type == "construct", 1e5, Link.Limit))
  
```



```{r}

NodeGraph <-trans2 %>%
  mutate(Node1 = Bus.1,
         Node2 = Bus.2) %>%
  select(Node1, Node2) %>%
  as.matrix() %>% 
  graph_from_edgelist(., directed = FALSE)

NodeGraph %>% 
  simplify(., remove.multiple = T, remove.loops = T) %>% 
  plot(.,vertex.size=.8, edge.arrow.size=.4, vertex.label = NA)
length(V(SubStatGraph2))

```

#Injection Vector
```{r}
InjectionVector <- trans1 %>% arrange(Bus.Name) %>% .$BusTransferB
```


#Create Impedance and Transmission matrix

parallel susceptances are added together. does this mean that when there are multiple lines connecting two nodes they should be added together and have the total capacity added together or should they be help seperate?

the removing of parallel cables may be causing some of the over capacity lines

```{r}
Impedance <- trans2 %>%
  mutate(Y = 1/X..Peak.Security.) %>%
  select(Bus.1, Bus.2, Y, Link)

```

#Alternative calc

```{r}

#checks that only inlcuded nodes are being counted
ValidNodes <- trans1 %>% 
  filter(Bus.Name %in% c(Impedance$Bus.1, Impedance$Bus.2)) 



#remove Slack bus, usually the largest generator
  SlackRef <- ValidNodes %>%
    arrange(Bus.Order) %>%
    summarise(Bus.Name = first(Bus.Name),
              Nodes = n())

PowerAlt <- PowerFlow(Impedance, ValidNodes, SlackRef)

PowerAlt2 <- trans2 %>%
  select( Link, Link.Limit, Link.Type, LineFlow__1 )%>%
  left_join(PowerAlt, ., by = "Link") %>%
  mutate(Over.Limit = abs(MW)>Link.Limit,
         Over.Limitx1.5 = abs(MW)>(Link.Limit*1.5)) %>%
  mutate(MW = round(MW),
         LineFlow__1= round(LineFlow__1),
         ratio = MW/LineFlow__1,
         diff  = MW-LineFlow__1,
         absdiff = abs(diff))


#corellation is strong enough, I am not going to focus on higher matching atm
cor(PowerAlt2$MW, PowerAlt2$LineFlow__1)

```

#Voltage Matching
Everyone matches to the same voltage unless it is a transformer.
There is an excpetion three types called construct also have different volatges, these could be also transformers under construction... this should be tested.


colours

green<- Transformer
orange <- 132
purple <- 275
Pink <- 400


```{r}

Vmatch <- trans1 %>% select(Bus.Name, Voltage)

Vnet <- trans2 %>% 
  select(Bus.1, Bus.2, Link.Type, Link) %>%
  left_join(., Vmatch, by = c("Bus.1"="Bus.Name")) %>%
  rename(Voltage.1 = Voltage) %>%
  left_join(., Vmatch, by = c("Bus.2"="Bus.Name")) %>%
  rename(Voltage.2 = Voltage) %>%
  mutate(Link.Voltage = as.factor(ifelse(Voltage.1 == Voltage.2, Voltage.1, 0)))

#Join with the Power2 data 

test <-trans1 %>% filter( Bus.Name %in% c("KEIT20", "KINT20"))

test <- PowerAlt2 %>%
  left_join(Vnet, by = "Link")

test2 <- test %>%
  filter(Link.Limit !=1e5) %>%
  group_by(Link.Voltage) %>%
  summarise(mean = mean(Link.Limit),
            sd = sd(Link.Limit),
            median = median(Link.Limit))

test %>% 
  filter(Link.Limit !=1e5) %>%
  ggplot(aes(x= Link.Voltage, y = Link.Limit)) +
  geom_boxplot()


library(RColorBrewer)

VoltCols <-  with(Vnet,
        data.frame(Link.Voltage = levels(Link.Voltage),
                   color = I(brewer.pal(nlevels(Link.Voltage), name = 'Dark2')))) %>%
  group_by(Bus.1, Bus.2) %>% #trying to stop the non-unique identifier problem
    mutate(Link = paste(Bus.1,Bus.2, 1:n(),sep = "-")) %>% #This allows multiple edges 
    #between the same node pair, it is not certain the data is always correct!
    ungroup 

Vnet <-   VoltCols %>%
  left_join(Vnet,.)

Vnet2 <- Vnet %>% filter(Voltage.1 != Voltage.2)

g <- graph.data.frame(Vnet[,1:2], vertices=Vmatch, directed=FALSE) #%>%
 # simplify(., remove.multiple = T, remove.loops = T) 
  
#V(g)$color <- V(g)$Voltage

#plot(g,vertex.size=5, edge.arrow.size=.4, vertex.label = NA)




E(g)$color<-Vnet$color

#Network colouored by voltage

set.seed(1530)
plot(g,vertex.size=1, edge.arrow.size=1, vertex.label = NA, main = "Grid by Link Voltage")


g <- delete_edges(g, (1:nrow(Vnet))[Vnet$Link.Voltage == 0] )

set.seed(1530)
plot(g,vertex.size=1, edge.arrow.size=1, vertex.label = NA, main = "Network of similar voltages")

#OverCapcity using my calcs

g <- graph.data.frame(Vnet[,1:2], vertices=Vmatch, directed=FALSE)
E(g)$color<-ifelse(PowerAlt2$Over.Limit, "red", "blue")

set.seed(1530)
plot(g,vertex.size=1, edge.arrow.size=1, vertex.label = NA, main = "Over Capacity My calc")
#Over Capacity Using grid calcs

E(g)$color<-ifelse(PowerAlt2$Over.Limit, "red", "blue")
set.seed(1530)
plot(g,vertex.size=1, edge.arrow.size=1, vertex.label = NA, main = "Over Capacity My calc")

#Amount of power flow

E(g)$color<- with(PowerAlt2,
        data.frame(levels = 10:1,
                   color = I(brewer.pal(10, name = 'RdYlBu'))))$color[ntile(PowerAlt2$MW, 10)]

set.seed(1530)
plot(g,vertex.size=0.5, edge.arrow.size=10, vertex.label = NA, main = "Mw deciles, Blue=low, Red=High")


```


```{r}
Volt.colours <- data.frame(Link.Voltage = unique(Vnet$Link.Voltage), Vcolour= brewer.pal(4, "Set1"))

g2 <- Vnet %>% 
  select(Bus.1, Bus.2, Link.Voltage) %>%
  left_join(., Volt.colours)
  


set.seed(10052016)
ggplot(data = g2, aes(from_id = Bus.1, to_id = Bus.2)) +
  geom_net( layout.alg = "kamadakawai", 
           size = 2, labelon = FALSE, vjust = -0.6, ecolour = g2$Vcolour,
           directed =FALSE, fontsize = 3, ealpha = 0.5) +
  xlim(c(-0.05, 1.05)) +
  theme_net() +
  theme(legend.position = "bottom")


```



Graph Stats

```{r}

NetworkStats <- function(g, colname = "value"){
data_frame(Metric = c("Nodes", "edges", "Components" ,"betweenness", "degree", "assortativity", "clustering", "distance"),
           value = c(vcount(g), ecount(g), components(g)$no, mean(betweenness(g)),mean(degree(g)), assortativity(g, degree(g)),
                     transitivity(g), 1)
) %>% setNames(c("Metric", colname))

#This takes forever maybe should replace with *distances* or something else? and custome electrical distance function
#  mean( ifelse(is.finite(shortest.paths(g)),shortest.paths(g), NA), na.rm = T)
}


test <-ifelse(is.finite(shortest.paths(gImp2)),shortest.paths(gImp2), NA)

mean(test, na.rm = T)
```



```{r}
gbase <- graph.data.frame(Impedance[,1:2], directed=FALSE)
gbase <- Impedance[,1:2] %>% 
  as.matrix %>%
  graph_from_edgelist( directed = FALSE)
#there is something rum going on here
gbase <- graph_from_data_frame(Impedance[,1:3], directed=FALSE)

get.edgelist(gbase) %>% as.tibble %>% filter(V1 == "PERS10")
as_data_frame(gbase) %>% filter(from == "PERS10")
get.edgelist(gbase2) %>% as.tibble %>% filter(V1 == "PERS10")
as_data_frame(gbase2) %>% filter(from == "PERS10")
test <- as_data_frame(gbase2)

  AZero <-  Impedance %>%
    CreateTransmission(., "Bus.1", "Bus.2")
  
  # #remove Slack bus, usually the largest generator
  # SlackRef<-which.max(ValidNodes$BusTransferA)

  A <- AZero[,colnames(AZero)!=SlackRef$Bus.Name]
  
  #Vreate the diagonal matrix of 
  C <- LinePropertiesMatrix(Impedance, "Bus.1", "Bus.2")
  
  B <- t(A) %*% C %*% A
  
ecount(gbasemean( ifelse(is.finite(shortest.paths(g)),shortest.paths(g), NA), rm.na =T))
B2 <- solve(B)
diag(B2)<-0
min(B2);max(B2)
Bvect <-unlist(B2)

gImp <- B2 %>% graph.adjacency(., mode="undirected", weighted=TRUE)
ecount(gImp)

min(E(gImp)$weight);max(E(gImp)$weight)

sum(E(gImp)$weight>2)

#Takes ages to calculate tells you where to cut off the edges.
# Edgedf <- data_frame(cutoff = seq(min(E(gImp)$weight), max(E(gImp)$weight), by = 1/100)) %>%
#   mutate(index = 1:n(),
#          Edges = cutoff %>%
#   map_dbl(~ sum(E(gImp)$weight>.x))
# )


RemoveEdges <- data_frame(valid = E(gImp)$weight > 3.733029) %>%
  mutate(index = 1:n()) %>%
  filter(valid == FALSE)

table(RemoveEdges$valid)

gImp2 <- gImp
gImp2 <- delete_edges(gImp, RemoveEdges$index)

plot(gImp2,vertex.size=1, edge.arrow.size=1, vertex.label = NA)

#keep just non isolated nodes
iso <- V(gImp2)[degree(gImp2)==0]
g2 <- delete.vertices(gImp2, iso)


  gX <- Impedance %>%
  graph.data.frame(., directed=FALSE)


DiffNetStats <- left_join(NetworkStats(gbase, "Topological"), NetworkStats(gImp2, "Impedance"), by= "Metric") %>%
  left_join(., NetworkStats(gX, "Reactance"), by= "Metric") %>%
  mutate_if(.,is.numeric, funs(format(round(.,3), scientific=F)) )

test <- distances(gbase)
test <- distances(gImp, weights = "Y")

```


#Simple Cascade

first try is to make a cascade of random failure until super componant collapses

An  importnant point is that there is re-balencing and smart re-balencing. with regular or dum re-balencing the rebalance occurs to try and match the demand of the whole component. This can cause further cables to trip making the cascade worse. Smart-rebalancing rebalences such that brown-outs occur forcing a demand reduction as generation is increaased ony to the point at which a line trip would occur.

This then raises the second point which is that cascades happen almost instantaneously mean demand and generation can't be rebalanced to any practical extent. In order for the power flow to work however there must be a balance, 

We need lit on the causes and effects of sudden imbalences

WHAT is this SNA stuff going on?

```{r}
#input networkas_adjacency_matrix(Impmat, attr = "weight")
gCasc <- gbase
#set an ImpedanceCascedge weight of 1
#gCasc <- set_edge_attr(gCasc, "weight", index = E(gCasc), 1 )

#node to delete rule
set.seed(193) #makes testing reproducible
deletevertex <- sample(V(gCasc)$name, 1)

#remove selected node from network
gCasc <- delete.vertices(gCasc, deletevertex)

#Create new impedance dataframe using the remaining edges
ImpedanceCasc<- as_tibble(get.edgelist(gCasc)) %>%
  #mutate(Y = edge_attr(gCasc, "weight")) %>%
  rename(Bus.1 = V1, Bus.2 = V2) %>%
  group_by(Bus.1, Bus.2) %>% #trying to stop the non-unique identifier problem
    mutate(Link = paste(Bus.1,Bus.2, 1:n(),sep = "-")) %>% #This allows multiple edges 
    #between the same node pair, it is not certain the data is always correct!
    ungroup %>%
left_join(., select(Impedance, Link, Y), by = "Link") %>%
  arrange(Link) 

#why is the test and the impedance data frames not equal?

ImpedanceCasc <- as_data_frame(gCasc) %>%
    rename(Bus.1 = from, Bus.2 = to) %>%
  group_by(Bus.1, Bus.2) %>% #trying to stop the non-unique identifier problem
    mutate(Link = paste(Bus.1,Bus.2, 1:n(),sep = "-")) %>% #This allows multiple edges 
    #between the same node pair, it is not certain the data is always correct!
    ungroup %>%
  mutate(Y = round(Y,7)) %>%
  select(Bus.1, Bus.2, Link, Y) %>%
  arrange(Link)

all_equal(test, ImpedanceCasc)

test2<- test %>% mutate(Y2 = ImpedanceCasc$Y) %>%
  filter(Y!=Y2) %>% mutate(diff = Y-Y2)
  

gbase <- graph_from_data_frame(Impedance[,1:3], directed=FALSE)
#test of Cascade
test <- Cascade(gbase, trans1, trans2)



(max(components(test)$csize)/vcount(gbase)) > 0.8

test %>% 
  simplify(., remove.multiple = T, remove.loops = T) %>% 
  plot(.,vertex.size=.8, edge.arrow.size=.4, vertex.label = NA)



```

Repeated Cascade

This function selects a node to delete deletes the node, performs the cascade calcs then if there is still a giant component deletes a new node and repeats
```{r}

gbase <- graph_from_data_frame(Impedance[,1:3], directed=FALSE)

EdgeDataTweaked <- trans2 %>%
  mutate(Link.Limit = case_when(
    Link == "BRAC20-BONB20-1" ~826,
    Link == "FAUG10-LAGG1Q-1" ~826,
    Link == "KEIT20-KINT20-1" ~826,
    Link == "LAGG1Q-MILW1S-1" ~826,
    TRUE ~ Link.Limit
    
  ))
  

test <- CalcOverLimit(gbase, trans1, EdgeDataTweaked)

EdgeDataTweaked %>%
  select(Link, Bus.1, Bus.2, Link.Limit) %>%
  filter(Link == "KEIT20-KINT20-1")

CascadeList<- Cascade(list(gbase), trans1, EdgeDataTweaked)

RandomAttack <-quo(sample(V(gbase)$name, 1))


FinalGrid <- AttackTheGrid(gbase, RandomAttack, trans1, trans2)

#Creates Gif of each step within the Cascade
dir.create("test")
set.seed(129)
CreateCascadeGif(CascadeList, file.path(basewd,"test"), "testme")



```

